---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LonCalGrowthAnalysis

<!-- badges: start -->
<!-- badges: end -->

The goal of LonCalGrowthAnalysis is to document the data and analysis conducted for: insert when paper is out.

## Installation

You can install the development version of LonCalGrowthAnalysis from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("KnechtTheDots/LonCalGrowthAnalysis")
```

## Example

We can see that the distribution of parental relative growth rates (RGR) is on the upper portion of the F2 RGRs. The purpose of this project is to learn something about the genetic architecture and if it contributes to reproductive isolation between the parents.

```{r example, message=FALSE}
library(LonCalGrowthAnalysis)
library(tidyverse)
# The phenotypes data set includes seedling phenotypes for 418 seedlings. 
# For example here is the distribution of F2 relative growth rates

phenotypes %>% 
  drop_na(rgr) %>% 
  filter(line != "F1") %>% 
  mutate(line = ifelse(line == "F2", "F2", "Parent"),
         line = factor(line, levels = c("Parent", "F2"))) %>% 
  ggplot(aes(x = rgr, fill = line)) +
  geom_histogram(bins = 20, color = "black") +
  scale_fill_manual(values = c("grey", "white")) +
  labs(x = "Relative Growth Rate",
       y = "",
       fill = "") +
  theme_minimal() +
  theme(legend.position = "inside",
        legend.position.inside = c(.25, .75),
        legend.direction = "horizontal",
        legend.box.background = element_rect(color = "black"))

```
